\documentclass[a4paper,11pt]{article}

\usepackage[55627]{MCMthesis}
\problem{E}
\usepackage{palatino}
\usepackage{url}
\usepackage[backend=bibtex, style=alphabetic]{biblatex}
\addbibresource{ref.bib}
\usepackage{subfigure}
%\bibliographystyle{alpha}
%\bibstyle{alpha}

\setlength\parskip{.5\baselineskip}

%\def\abstractname{Abstract}

\title{A Metric Based on smart growth principles and map partitioning}
\author{\small Chenjie Yu, Chen Cheng, Ziheng Chen }
\date{\today}
\begin{document}
\begin{abstract}
Based on the ten smart growth principles in `The Smart Growth Network', we set a smart growth metric which can well measure how successfully a city develops.
To define a metric according to the smart growth principles, we divide a certain city into multiple square units, classifying them as one of following regional types: residential area, recreational area, working area, open space, or undeveloped area. After setting the development level for each square unit respectively, we define the metric by merging the ten principles into four judging standards: mix land use, open space and landscape, housing choice, and transportation convenience. Then we give the city a score considering all four judge standards.
We select Nottingham and Barrie as our subjects. We collect the data of the two cities with the help of Google map and OpenStreetMap, and then research their current growth plan. After that, we use our metric to assess the current growth plan, and utilize greedy method to develop a growth plan for both cities over the next 30 years. According to our growth plan, we sort all the factors in the order of potential and compare their ranking between the two cities.
Finally, we modificate the model according to both cities' population growth, re-establish the growth plan for the two cities, then point out the limitations of smart growth principles in nowadays society.
  \begin{keywords}
    city development; smart growth; map partitioning
  \end{keywords}
\end{abstract}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}
\newpage

\tableofcontents
\newpage
\pagestyle{fancy}
\setcounter{page}{1}

\input{body.tex}

\end{document}
